Data Management \\ and LSST Special Programs

### 2021-11-27 DMTN-065.tex
removed reference to DM-12575

The above statements of intent are derived from the Data Management Subsystem Requirements document, \citeds{LSE-61}, which contains several requirements related to the processing of data from Special Programs (DMS-REQ-0069, 0320, 0321, 0322, and 0344). To ensure that the work-hours needed to reconfigure and test the pipelines, and run them and verify the data products for public release (which may potentially be needed on intermediate timescales that do not coincide with the Prompt/Yearly timescales, e.g., monthly stacks of deep drilling fields), have been included in the personnel budget, JIRA ticket DM-12575 is currently under consideration.

>>>>

The above statements of intent are derived from the Data Management Subsystem Requirements document, \citeds{LSE-61}, which contains several requirements related to the processing of data from Special Programs (DMS-REQ-0069, 0320, 0321, 0322, and 0344). 
Ensuring that the work-hours needed to reconfigure and test the pipelines, to run them and to verify and validate the data products for public release (which may potentially be needed on intermediate timescales that do not coincide with the Prompt/Yearly timescales, e.g., monthly stacks of deep drilling fields), is the role of Operations.
